COG-ED Manuscript

### 2022-01-21 06_Paper/COG-ED/Manuscript.Rmd
eta2, CIs, and rounded BFs for all ANOVAs

`r apa_print(hypothesis1a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`

@@

`r apa_print(hypothesis1b_rmanova)$full_result`

@@

`r apa_print(hypothesis1c_mental_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_mental_BF)$bf`

@@

`r apa_print(hypothesis1c_physical_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_physical_BF)$bf`

@@

`r apa_print(hypothesis1c_time_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_time_BF)$bf`

@@

`r apa_print(hypothesis1c_performance_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_performance_BF)$bf`

@@

`r apa_print(hypothesis1c_effort_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_effort_BF)$bf`

@@

`r apa_print(hypothesis1c_frustration_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_frustration_BF)$bf`

@@

`r apa_print(hypothesis2a_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis2a_BF)$bf`

>>>>

`r apa_print(hypothesis1a_rmanova)$statistic`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1a_BF)$bf, digits = 2)`

@@

`r apa_print(hypothesis1b_rmanova)$statistic`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1b_rmanova$anova_table[1,"F"], df = hypothesis1b_rmanova$anova_table[1,"num Df"], df_error = hypothesis1b_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1b_rmanova$anova_table[1,"F"], df = hypothesis1b_rmanova$anova_table[1,"num Df"], df_error = hypothesis1b_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1b_BF)$bf, digits = 2)`

@@

`r apa_print(hypothesis1c_mental_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_mental_rmanova$anova_table[1,"F"], df = hypothesis1c_mental_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_mental_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_mental_rmanova$anova_table[1,"F"], df = hypothesis1c_mental_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_mental_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_mental_BF)$bf, digits = 2)`

@@

`r apa_print(hypothesis1c_physical_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_physical_rmanova$anova_table[1,"F"], df = hypothesis1c_physical_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_physical_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_physical_rmanova$anova_table[1,"F"], df = hypothesis1c_physical_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_physical_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_physical_BF)$bf, digits = 2)`

@@

`r apa_print(hypothesis1c_time_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_time_rmanova$anova_table[1,"F"], df = hypothesis1c_time_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_time_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_time_rmanova$anova_table[1,"F"], df = hypothesis1c_time_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_time_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_time_BF)$bf, digits = 2)`

@@

`r apa_print(hypothesis1c_performance_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_performance_rmanova$anova_table[1,"F"], df = hypothesis1c_performance_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_performance_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_performance_rmanova$anova_table[1,"F"], df = hypothesis1c_performance_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_performance_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_performance_BF)$bf, digits = 2)`

@@

`r apa_print(hypothesis1c_effort_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_effort_rmanova$anova_table[1,"F"], df = hypothesis1c_effort_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_effort_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_effort_rmanova$anova_table[1,"F"], df = hypothesis1c_effort_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_effort_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_effort_BF)$bf, digits = 2)`

@@

`r apa_print(hypothesis1c_frustration_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_frustration_rmanova$anova_table[1,"F"], df = hypothesis1c_frustration_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_frustration_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_frustration_rmanova$anova_table[1,"F"], df = hypothesis1c_frustration_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_frustration_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_frustration_BF)$bf, digits = 2)`

@@

`r apa_print(hypothesis2a_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis2a_BF)$bf, digits = 2)`
